### 2017-06-13 Docs/Thesis/docs/chapter6.tex
d

In this section we present some ideas for future works and implementation for SIMITAR. On the first section "Improoving results", we suggest approaches for improving the current results. They include calibration of some constants, finer controll of packet injection, and performance improovments.

\subsection{Improoving results}

@@

	\item \texttt{DataProcessor::m\_session\_cut\_time}:  this member is responsible for defining whaterver a file transfecence still active or has ended. It defines the minimum OFF timme acceptable.

>>>>

%2nd review
In this section we present some ideas for future works and implementation for SIMITAR. On the first section "improving results" we point some approaches for improving the current results. They include calibration of constants, finer control of packet injection, and performance improvement.

\subsection{Improving results}

@@

	\item \texttt{DataProcessor::m\_session\_cut\_time}:  this member is responsible for defining whaterver a file transfecence still active or has ended. Baically it define the ON and OFF times.
